Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-26 index.Rmd
first draft ORA project summary, fixed code mistake manuscript, minor changes GSPA poster+abstract
changes discussion slide

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanthemer)
library(xaringanExtra)
library(icons)
library(widgetframe)
library(DiagrammeR)

@@

# Conclusion

`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**, but...

@@

`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.5, fill = "#035AA6")` $~~$ It's highly **resource-intensive**  
--

`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**     
--

`r icon_style(icons::fontawesome("question-circle"), scale = 1.6, fill = "#035AA6")` $~~$ Surprisingly, even **multiple, consistent estimates may backfire**   
--

## Future directions
`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
--

>>>>

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanthemer)
library(xaringanExtra)
library(icons)
library(widgetframe)

@@

.center[
### **Compared to a single estimate, we find no evidence that crowd estimates improve lay perceptions of scientific findings**
]

@@

## Future directions
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "#035AA6")` $~~$ Does **variability aversion** explain the findings?

We conclude that, compared to a single estimate, we do not find evidence that crowd estimates improve lay perceptions of scientific findings. In the future, we are curious to explore whether it might be aversion to variability that explains these findings, and what the perceptions of scientists are. We also believe that in the future it is important for crowd scientists to consider how -- for example, by drawing from research on science communication -- to tackle science skepticism and effectively communicate variable crowd estimates to lay consumers.  
--

`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
--
